---
title: "Assignment 1: R Basics"
author: "Your name and student ID"
date: "Today's date"
output: pdf_document
---

### Instructions 
* Complete this assignment.
* Instructions for submission.
* Due date:

```{r setup, include = FALSE}
# Don't change these lines, just run them!
source("setup/hw01.RAGS.R")
```

\newpage

**1. [2 points] Assign two integers of your choosing to the values x and y such that they sum to 10.**

```{r}
x <- "<<<<YOUR CODE HERE>>>>"
y <- "<<<<YOUR CODE HERE>>>>"

# BEGIN SOLUTION
x <- 2
y <- 8
# END SOLUTION

check_problem1()
```

\newpage


**2. [1 point] Assign the product of x and y to a variable z.**

```{r}
z <- "<<<<YOUR CODE HERE>>>>"

# BEGIN SOLUTION
z <- x * y
# END SOLUTION

check_problem2()
```
\newpage

**3. [1 point] What function do we use to load packages?**
```{r}
# p3 <- "load"
# p3 <- "library"
# p3 <- "package"
# p3 <- "read"

# BEGIN SOLUTION
p3 <- "library"

# END SOLUTION
check_problem3()
```

\newpage

**4. [1 point] Load the nycflights13 package and assign subsetFlights to the first 10 rows of the `flights` dataset.**
```{r}
library(nycflights13)
subsetFlights <- "<<<<YOUR CODE HERE>>>>"

# BEGIN SOLUTION
subsetFlights <- flights[1:10,]

# END SOLUTION
check_problem4()
```

**5. [1 point] What are you looking forward to learning in this class?**

// BEGIN SOLUTION

Looking forward to learning lots! :)

// END SOLUTION

### Check your score
```{r check-total-score}
# Just run this chunk.
total_score()
```

