---
title: "Assignment 1: R Basics"
author: "Your name and student ID"
date: "Today's date"
output: pdf_document
---

### Instructions 
* Complete this assignment.
* Instructions for submission.
* Due date:

```{r setup, include = FALSE}
# Don't change these lines, just run them!
source("setup/hw01.RAGS.R")
```

\newpage

**1. [2 points] Assign two integers of your choosing to the values x and y such that they sum to 10.**

```{r}
x <- "<<<<YOUR CODE HERE>>>>"
y <- "<<<<YOUR CODE HERE>>>>"

# BEGIN SOLUTION
x <- 2
y <- 8
# END SOLUTION

check_problem1()
```

\newpage


**2. [1 point] Assign the product of x and y to a variable z.**

```{r}
z <- "<<<<YOUR CODE HERE>>>>"

# BEGIN SOLUTION
z <- x * y
# END SOLUTION

check_problem2()
```
\newpage

**3. [1 point] What function do we use to load packages?**
```{r}
# p3 <- "load"
# p3 <- "library"
# p3 <- "package"
# p3 <- "read"

# BEGIN SOLUTION
p3 <- "library"

# END SOLUTION
check_problem3()
```

\newpage

**4. [1 point] Load the nycflights13 package and assign subsetFlights to the first 10 rows of the `flights` dataset.**
```{r}
library(nycflights13)
subsetFlights <- "<<<<YOUR CODE HERE>>>>"

# BEGIN SOLUTION
subsetFlights <- flights[1:10,]

# END SOLUTION
check_problem4()
```

**5. [1 point] What are you looking forward to learning in this class?**

// BEGIN SOLUTION

Looking forward to learning lots! :)

// END SOLUTION

### Check your score
```{r check-total-score}
# Just run this chunk.
total_score()
```


### Submission

For assignments in this class, you'll be submitting using the **Terminal** tab in the pane below. In order for the submission to work properly, make sure that:

1. Any image or data files you add that are needed to knit the file are in the `src` folder and file paths are specified accordingly. 
2. You **have not changed the file name** of the assignment.
3. The file knits properly.

Once you have checked these items, you can proceed to submit your assignment.

1. Click on the **Terminal** tab in the pane below.
2. Copy-paste the following line of code into the terminal and press enter.

cd; cd ph101-fa20/hw/hw01; python3 turn_in.py

3. Follow the prompts to enter your Gradescope username and password.
4. If the submission is successful, you should see "Submission successful!" appear as output.
5. If the submission fails, try to diagnose the issue using the error messages--if you have problems, post on Piazza under the post "Submission Issues".
6. Follow the provided links to make sure your submission on Gradescope is as intended.
